\section{Sk8er Boi}
\begin{multicols}{2}
\begin{guitar}

	[D]He was a b[A]oy, she was a g[Bm]irl
	Can I make it an[Bb]ymore obvious?
	[D]He was a p[A]unk, and she did b[Bm]allet
	What m[C]ore can I say?
	[D]He wanted h[A]er, she'd never t[Bm]ell,
	Secretly s[Bb]he wanted him as well.
	[D]But all of the frie[A]nds, stuck up their n[Bm]ose,
	They had a pr[C]oblem with his baggy clothes.

	
	CHORUS
	[F]He was a sk[C]ater boy, she said see ya l[Bb]ater boy,
	He wasn't g[A]ood enough for her
	[F]She had a pr[C]etty face, but her head was [Bb]up in spaces, 
	She needed to[A] come back down to[Bb] earth

	
	Five years from now, she sits at home,
	Feeding the baby she's all alone.
	She turns on TV, guess who she sees,
	Skater boy rockin' up MTV.
	She calls up her friends, they already know,
	They've all got tickets to see his show.
	She tags along, and stands in the crowd,
	Looks up at the man that she turn dooowwnnnn.


	CHORUS
	He was a skater boy, she said see ya later boy
	He wasn't good enough for her.
	Now he's a superstar, slammin' on his guitar
	Does your pretty face see what he's worth?
	He was a skater boy, she said see ya later boy,
	He wasn't good enough for her.
	Now he's a superstar, slammin' on his guitar
	Does your pretty face see what he's worth?


	F C Bb Db 2x


	[D]Sorry girl but you missed [F]out,
	[F]Well tough luck that boy's mine n[C]ow.
	[C]We are more than just good f[Bb]riends,
	This is [A]how the story en[D]ds.
	[D]Too bad that you couldn't s[F]ee,
	[F]See the man that boy could [C]be.
	[C]There is more than meets the [Bb]eye,
	I see the s[A]oul that is in[D]side.


	[D]He's just [A]a boy, and I'm just a g[B]irl,
	Can I make it an[Bb]ymore obvious?
	[D]We are in lo[A]ve, ha[B]ven't you heard?
	How we r[C]ock each other's world?

	
	CHORUS:
	I'm with the skater boy, I said see ya later boy,
	I'll be back stage after the show.
	I'll be at out studio, singing the song he wrote,
	About the girl you used to know.
	I'm with the skater boy, I said see ya later boy,
	I'll be back stage after the show.
	I'll be at out studio, singing the song he wrote,
	About the girl you used to know.
\end{guitar}
\end{multicols}
